Comparative study of Dask and Spark for neuroimaging pipelines

### 2019-06-10 latex/acl2019.tex
Modified exp1 - # of splits

%% Iterations
\subsection{Experiment 1: Number of iterations}
In Figure \ref{fig:inc_itr} we see that spark and the dask bag api are equivalent in
term of performance. The dask delayed api seems to perform well with low amount of
task but grow faster the spark and dask bag. We think this is because dask delayed
often schedule a block on different worker of the same instance which cause small
delay everytime due to inter worker communication. This is good when there is fewer
tasks as is make the io between block go out of sync hence lowering the io bottleneck
observed earlier however as the number of tasks increases those small delays become
significant. The dask futures api seems to outperform all the other apis but this is
most likely because the tasks are not inter dependent thus this application benifits
from the less optimal but faster scheduling brought by dask futures.

@@

% Chunks
\subsection{Experiment 1: Number of splits}
In Figure \ref{fig:inc_chunk} Spark is not compared for 30 chunks. This is because
spark has a 2GB limitation in the task size it can compute. All API have a longer
make span at 30 chunks compared to 125 chunks. This is because the 8 instances each
have 8 cores thus merely half the resources available are used. At 125 chunks Dask
bag are the fastest. This could be explained by Dask bag having the better
optimization of the Dask's API and that Spark has to perform serialization to Java.
At 750 chunks Spark becomes as good

@@

    \subfloat[Incrementation total time]{%
      \includegraphics[clip,width=\columnwidth]{images/inc_idle_splits.png}%
    }
    \caption{10 iterations, 4 sec. sleep delay, 8 instances}
    \label{fig:inc_chunk}
\end{figure}

>>>>

%% Iterations
\subsection{Experiment 1: Number of iterations}
In Figure \ref{fig:inc_itr} we see that spark and the dask bag api are equivalent in
term of performance. The dask delayed api seems to perform well with low amount of
task but grow faster the spark and dask bag. We think this is because dask delayed
often schedule a block on different worker of the same instance which cause small
delay everytime due to inter worker communication. This is good when there is fewer
tasks as is make the IO between block go out of sync hence lowering the IO bottleneck
however as the number of tasks increases those small delays become significant. The
dask futures api seems to outperform all the other apis but this is most likely
because the tasks are not inter dependent thus this application benifits from the
less optimal but faster scheduling brought by dask futures.

@@

% Chunks
\subsection{Experiment 1: Number of splits}
In Figure \ref{fig:inc_splits} Spark is not compared for 30 chunks. This is because
spark has a 2GB limitation in the task size it can compute. Note from Figure
\ref{fig:inc_splits}(b) that the compute time increase when there is more splits.
This is expected because the sleep delay is constant throughout this experiment and
there are more compute task when the number of splits increases. We also note that in
Figure \ref{fig:inc_splits}(b) for 30 splits the dask bag api has a much lower
overhead time. This is because calculate the idle time of active worker only and the
dask bag api was only using one worker per split in comparison to the dask delayed
and dask futures api which were offloading the calculations on multiple workers on a
same instance. From Figure \ref{fig:inc_splits} we observe that when the dataset is
seperated in more (smaller) splits it saves IO time however it increases the overhead
by a similar amount; the inverse happens when we reduce teh number of splits.

@@

    \subfloat[Incrementation total time]{%
      \includegraphics[clip,width=\columnwidth]{images/inc_idle_splits.png}%
    }
    \caption{10 iterations, 4 sec. sleep delay, 8 instances}
    \label{fig:inc_splits}
\end{figure}
